Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta

### 2020-10-08 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/ms.tex
added supp mat. section

The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}

>>>>

  The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.
  Insets: A blowup of the corresponding subfigure in the range $p_{\mathrm{r}}=0 - 0.7$ GeV/c.}

### 2020-10-08 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/supp_original.tex
added supp mat. section

>>>>

\section{\large Deuteron Kinematic Distributions }
\noindent Figures show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}, 45^{\circ}$.
The data has been normalized by the total charge and corrected for the inefficiencies described in the Letter.  
\includegraphics[scale=0.4]{plots/d2_kin_thnq35.png}
\caption{Deuteron kinematic distributions for the 80 (blue), 580 (red) and 750 (magenta) MeV/c cental missing momentum settings at $\theta_{nq}=35^{\circ}$.}
\includegraphics[scale=0.35]{plots/d2_kin_thnq45.png}
\caption{Same as Fig. \ref{}, but for $\theta_{nq}=45^{\circ}$}

### 2020-10-08 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
added PRL reply
added supp mat. section

\includegraphics[scale=0.30]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}

@@

@@

\indent Figure \ref{fig:fig8} shows the missing energy spectrum for the 580 MeV/c setting (left) and the corresponding reconstructed SHMS $z$-vertex (right) for the specified

@@

kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:fig9}. The calculation was done using the

@@

Fig. \ref{fig:fig10}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section.

@@

\indent Figure \ref{fig:fig11} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
In Fig. \ref{fig:fig11}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,

@@

\caption{Same as Fig. \ref{fig:fig12} but for bin-centering corrections.}

@@

Figures \ref{fig:fig12} and \ref{fig:fig13} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that

@@

kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:fig14} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in

@@

>>>>

\includegraphics[scale=0.33]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}

@@

\section{\large Deuteron Kinematic Distributions }
\noindent Figures \ref{fig:fig8} and \ref{fig:fig9} show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$.
The data has been normalized by the total charge and corrected for the inefficiencies described in the Letter. Radiative and bin-centering corrections have not been applied for these plots.
The same event selection cuts mentioned in the previous sections were applied (including the $Q^{2}$ cut), with the exception of the $Q^{2}$ distribution itself.
Only the first dataset (out of 2) for the 580 and (out of 3) for the 750 MeV/c settings are shown. 
\includegraphics[scale=0.4]{plots/d2_kin_thnq35.png}
\caption{Deuteron kinematic distributions for the 80 (blue), 580 (set1, red) and 750 (set1, magenta) MeV/c cental missing momentum settings at $\theta_{nq}=35^{\circ}$.}
\includegraphics[scale=0.35]{plots/d2_kin_thnq45.png}
\caption{Same as Fig. \ref{fig:fig8}, but for $\theta_{nq}=45^{\circ}$}

@@

\indent Figure \ref{fig:fig10} shows the missing energy spectrum for the 580 MeV/c setting (left) and the corresponding reconstructed SHMS $z$-vertex (right) for the specified

@@

kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:fig11}. The calculation was done using the

@@

Fig. \ref{fig:fig12}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section.

@@

\indent Figure \ref{fig:fig13} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
In Fig. \ref{fig:fig13}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,

@@

\caption{Same as Fig. \ref{fig:fig14} but for bin-centering corrections.}
\label{fig:fig15}

@@

Figures \ref{fig:fig14} and \ref{fig:fig15} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that

@@

kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:fig16} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in

@@

\label{fig:fig16}
